%\section{References}

\begin{thebibliography}{1}

\bibitem{Olga2022}  Latent Class Cluster Analysis: Selecting the number of clusters
https://www.sciencedirect.com/science/article/pii/S2215016122001273

\bibitem{CDCDataset}Dietary Patterns of Patients with Chronic Kidney Disease: The Influence of Treatment Modality
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6723967/

\bibitem{Zheng2021} Subtyping CKD Patients by Consensus Clustering: The Chronic Renal Insufficiency Cohort (CRIC) Study: https://jasn-asnjournals-org.libaccess.lib.mcmaster.ca/content/32/3/639

\bibitem{LockWood2020} Physical Symptom Cluster Subgroups in Chronic Kidney Disease
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7353908/

\bibitem{USRDS2022} United States Renal Data System. https://www.niddk.nih.gov/about-niddk/strategic-plans-reports/usrds . This site will have agw group based CKD studies and reports.


\bibitem{Chen2016}  	Chen X, Wei G, Jalili T, Metos J, Giri A, Cho ME, Boucher R, Greene T, Beddhu S: The associations of plant protein intake with all-cause mortality in CKD. Am J Kidney Dis 67: 423–430, 2016 (26)

\bibitem{Liu2019} [26]	Liu, Hao-Wen; Tsai, Wen-Hsin; Liu, Jia-Sin; Kuo, Ko-Lin. 2019. "Association of Vegetarian Diet with Chronic Kidney Disease." Nutrients 11, no. 2: 279.

\bibitem{Aleix2019} Aleix Cases, Secundino Cigarran-Guldris, Sebastian Mas, and Emilio Gonzalez-Parr. Vegetable-Based Diets for Chronic Kidney Disease? It Is Time to Reconsider. Nutrients. 2019 Jun; 11(6): 1263.

\bibitem{Gutierrez2014} Gutierrez O.M., Muntner P, Rizk D.V., McClellan W.M., Warnock D.G., Newby P.K., Judd S.E.: Dietary patterns and risk of death and progression to ESRD in individuals with CKD: A cohort study. Am J Kidney Dis 64: 204–213, 2014  (27)

\bibitem{Huang2013} Huang X., Jime nez-Moleo J. J., Lindholm B., Cederholm T., Arnoldv J., Rise rus U., Sjogren P., Carrero J. J.: Mediterranean diet, kidney function, and mortality in men with CKD. Clin J Am Soc Nephrol 8: 1548–1555, 2013 (28)

\bibitem{Ricardo2013} Ricardo A. C., Madero M., Yang W., Anderson C., Menezes M., Fischer M.J., Turyk M., Daviglus M.L., Lash J.P.: Adherence to a healthy lifestyle and all-cause mortality in CKD. Clin J Am Soc Nephrol 8: 602–609, 2013 (30)

\bibitem{Tsuruya2015} Tsuruya K., Fukuma S., Wakita T., Ninomiya T., Nagata M., Yoshida H., Fujimi S., Kiyohara Y., Kitazono T., Uchida K., Shirota T., Akizawa T., Akiba T., Saito A., Fukuhara S.: Dietary patterns and clinical outcomes in hemodialysis patients in Japan: A cohort study. PLoS One 10: e0116677, 2015 (31)

\bibitem{Ricardo2015} Ricardo A.C., Anderson C.A., Yang W., Zhang X., Fischer M. J., Dember L. M., Fink J. C., Frydrych A., Jensvold N. G., Lustigova E., Nessel L. C., Porter A. C., Rahman M., Wright Nunes J. A., Daviglus M. L., Lash J. P.;  CRIC Study Investigators: Healthy lifestyle and risk of kidney disease progression, atherosclerotic events, and death in CKD: Findings from the Chronic Renal Insufficiency Cohort (CRIC) Study. Am J Kidney Dis 65: 412–424, 2015 (17)

\bibitem{Asghari} Golaleh Asghari, Mehrnaz Momenan, Emad Yuzbashian, Parvin MirmiranEmail author and Fereidoun Azizi. Dietary pattern and incidence of chronic kidney disease among adults: a population-based study

\bibitem{CDCDataset} CDC data on: Demographics, Dietary Survey, Examination, Laboratory, Questions. https://wwwn.cdc.gov/nchs/nhanes/Search/DataPage.aspx?Component=Dietary


\bibitem{Ahmed2019} Sayed Ahmed, Youcef Derbal: Effect of Dietary Patterns on CKD Mortality, and Impact of Dietary Recommendations Shift on Chronic Kidney Disease: $https:// www.researchgate.net/ publication/ 337544477\_Effect\_of \_Dietary\_Patterns\_on \_CKD \\ \_Mortality \_and \_Impact\_of\_Dietary \_Recommendations \_Shift\_on\_Chronic\_Kidney \_Disease$








\end{thebibliography}